---
title: "Average monthly river flow from hydroelectric plants"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cerulean
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(ggplot2)
library(tidyverse)
library(zoo)
library(plotly)
library(dplyr)
library(stringr)

load("app_hid-FORECAST1step.RData")
load("app_hid.RData")
nome<-c("14 DE JULHO","BARRA GRANDE","CAMPOS NOVOS", 
        "CASTRO ALVES","D. FRANCISCA","ERNESTINA",    
        "FUNDÃO","ITAUBA","JACUI","MONJOLINHO",  
        "MONTE CLARO","PASSO FUNDO","PASSO REAL",                      "QUEBRA QUEIXO","SALTO PILAO","SAO JOSE")
colnames(dados)<-nome

```

Plots
=====================================    
Inputs {.sidebar}
---
```{r}
inputPanel(
selectInput("HydPlants", label = "Select one hydroelectric plants to visualize", choices = sort(nome), selected = "14 DE JULHO")
)

```

Column {}
-----------------------------------------------------------------------

### Observed RF and fitted values

```{r}
renderPlot({
  j<-which(nome == input$HydPlants)
  y<-na.omit(dados[,input$HydPlants])
  s<-12
  h=12
  y <- zoo(y, order.by = datas)
  y <- aggregate(y, as.yearmon, mean)
  y<-y/1000
  y<-ts(y[1:(length(y)-h)],frequency = s,start=c(2010,1))
  y[y==0] <- mean(y, na.rm = TRUE)
  
  plot(y,main="",ylim=c(min(y),max(y)+0.25),ylab="RF")
    lines(ts(final[[j]]$fitted,frequency = 12,start = c(2010,1)), col=2,lty=2,lwd=2)
    lines(ts(final_Ray[[j]]$fitted,frequency = 12,start = c(2010,1)),col=5,lty=3,lwd=1.7)
    lines(final_GAMMA[[j]]$fitted, col=6,lty=4,lwd=1.6)
    legend("top",
        c("Original","BXII-GAS","Ray-GAS","gamma-GAS"), 
        col = c(1,2,5,6), 
        lty= c(1,2,3,4), 
        lwd = c(1,2,1.7,1.6), 
        bty="n", cex = 1)
})

```

### Out-of-sample BXII-GAS forecasts 1-step ahead, updated by actual observations

```{r}
renderPlot({
  j<-which(nome == input$HydPlants)
  h=12
  s=12
  y_prev<-get(paste0("y_prev",j))
  plot(ts(y_prev,frequency = s,start =c(2023,9)),
       ylab="RF",ylim=c(min(y_prev,out_forecast[,1,j]),max(y_prev,out_forecast[,1,j])))
  lines(ts(out_forecast[,1,j],frequency = s,start = c(2023,9)),col=2,lty=2,lwd=2)
  legend("topright", 
           c("BXII-GAS"),
           col = c(2),
           lty= c(2),
           lwd = c(2), bty="n", cex = 1)
})
```

Column {}
-----------------------------------------------------------------------
### Monthplot for the RF time series

```{r}
renderPlot({
  j<-which(nome == input$HydPlants)
  y<-na.omit(dados[,input$HydPlants])
  s<-12
  h=12
  y <- zoo(y, order.by = datas)
  y <- aggregate(y, as.yearmon, mean)
  y<-y/1000
  y<-ts(y[1:(length(y)-h)],frequency = s,start=c(2010,1))
  y[y==0] <- mean(y, na.rm = TRUE)
  
  monthplot(y,main="",ylab="RF")
})
```

### Autocorrelation function (ACF) of the BXII-GAS residual

```{r}
renderPlot({
  j<-which(nome == input$HydPlants)
  acf(final[[j]]$residuals,main="")
})

```

Tables
=====================================  

### Information criteria and accuracy measures

```{r}
resultados<-cbind(nome,results)
colnames(resultados)<-c("hydroelectric plants","AIC-BXII","AIC-RAy","AIC-GAMMA"
                  ,"MAE-BXII","MAE-Ray","MAE-GAMMA"
                  ,"MAPE-BXII","MAPE-Ray","MAPE-GAMMA"
                  ,"RMSE-BXII","RMSE-Ray","RMSE-GAMMA"
                  ,"pv-LB-BXII","pv-LB-Ray","pv-LB-GAMMA"
                  )
renderTable(resultados)
```


### Forecasting performance comparison

```{r}
resultados1<-cbind(nome,results_out)
colnames(resultados1)<-c("hydroelectric plants","MAE-BXII","MAE-Ray","MAE-GAMMA"
                  ,"RMSE-BXII","RMSE-Ray","RMSE-GAMMA"
                  ,"MAPE-BXII","MAPE-Ray","MAPE-GAMMA"
                  )
renderTable(resultados1)
```

About
=====================================
**Goals**


**The data**



**Source files**


**Author**

***Name:*** Fernando José Monteiro de Araújo

***Filiation:*** Universidade Federal do Rio Grande do Sul - UFRGS, Departamento de Estatı́stica.

***Email:*** fernando.monteiro@ufrgs.br

***Orcid ID:***

***Scopus Author ID:*** 

***ResearcherID (Publons):*** 

**Reference**


